Instructions for developing new pages for the MarineOmics webpage

### 2023-12-15 DRAFT_DNA_methylation.Rmd
Update DRAFT_DNA_methylation.Rmd
added citation to vert image

[ placeholder for Kathryn to add some stuff! ]

>>>>

```{r meth-vert, echo = FALSE, out.width = "70%", fig.align = "center", fig,cap= "Genome screenshots of methylation quantified in 2kb running windows over the first 3Mb of chromosome 1 zebrafish and mouse, and of the largest scaffold (NW_006890054.1) in elephant shark (doi: 10.12688/f1000research.11281.1)"}
knitr::include_graphics("DRAFT_DNA_methylation/vert_methyl_distr.png")
```
[ placeholder for Kathryn to add some stuff! ]
